Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-05-08 Ben_Manuscripts/transport/Draft.tex
Intro edits

  The uniform size and complex chemical topology of the pores that 
  constitute cross-linked inverted hexagonal (H\textsubscript{II})
  phase lyotropic liquid crystal (LLC) membranes make them promising
  candidates for selective separation membranes. 
  %MRS3: I do worry that the above makes it look like we are not acknowledging
  %the formulation problems.  Maybe something like: ''models of how chemically
  %selective separation membranes could can function''?  So the focus is more
  %on the science that these membranes could reveal, rather than saying they
  %are good membranes now?  Then we talk about new membranes at the end of the
  %introduction. Thoughts? I didn't go ahead and make  the change since it
  %needs a bit more thought.  I'm open to other ways to reformulate.  Some of
  %this thinking will percolate into the rest of the introduction as well.
  In this work, we observe transport
  of water, sodium ions and 20 small polar solutes within the pores 
  of an LLC membrane using atomistic molecular simulations. We 
  find that the transport of a species is dependent not only on 
  molecular size, but on chemical functionality as well. The 
  membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. We observe
  that all solutes perform intermittent hops between lengthy
  periods of entrapment. Three different trapping mechanisms are 
  responsible for this behavior. First, solutes that drift
  out of the pore can become entangled among the dense monomer
  tails. Second, solutes can donate hydrogen bonds to the monomer
  head groups. Third, solutes can coordinate with sodium counter ions.
  The degree to which a solute is affected by each mechanism is 
  dependent on the chemical functionality of the solute. Using the
  insights developed in this study, we can begin to think about 
  how to redesign existing LLC membranes in order to perform 
  solute-specific separations.

@@

  Under the right conditions, amphiphilic molecules can self-assemble
  into ordered nanostructures that may be capable of performing highly
  selective separations.
  \begin{itemize}
    \item The uniform-sized aqueous pores characteristic of these types of
    systems enforce a molecular-size cut-off, eliminating issues related to the
    polydisperity of NF pores.
    \item By controlling the chemical identity of moeties inside the pores, 
    it may be possible to tune these types of materials for solute-specific
    separations.
  \end{itemize}

  Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I 
  bicontinuous (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
  phases.
  \begin{itemize}
	\item When cross-linked, these materials can function as separations
	 membranes.
	\item The H\textsubscript{II} phase has hexagonally packed, straight
	pores which is the ideal geometry for high throughtput separations.
	\item However, the synthesis of H\textsubscript{II} membranes with 
	highly aligned hexagonal mesophases has been a challenge that has 
	prevented this type of membrane's viability.
	\item The Q\textsubscript{I} has been studied with much more 
	success. 
  \end{itemize}

@@

  In this work, we present studies of the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character. Figure~\ref{fig:membrane_rendering} shows an atomistic rendering of
  the membrane in which we placed solutes. We have listed the solutes studied along with the abbreviations that
  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
  Note that, in order limit our studies to uncharged species, we have only studied
  acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
  pKa of acetic acid is 4.75.~\cite{chuysinuan_gallic_2009,perrin_pka_1981} 
  Assuming that the pKa of gallic acid is similar to NaGA3C11, it is possible
  for our sodium salted monomer to exist at the same time as protonated acetic
  acid. In any case, we are more interested in mechanisms of interaction with
  specific chemical functionality more than the behavior of specific molecules.

>>>>

  The uniform size and complex chemical topology of the pores formed by
  self-assembled amphiphilic molecules such as liquid crystals make them
  promising candidates for selective separations.
  %that 
  %constitute cross-linked inverted hexagonal (H\textsubscript{II})
  %phase lyotropic liquid crystal (LLC) membranes make them promising
  %candidates for selective separation membranes. 
  %MRS3: I do worry that the above makes it look like we are not acknowledging
  %the formulation problems.  Maybe something like: ''models of how chemically
  %selective separation membranes could can function''?  So the focus is more
  %on the science that these membranes could reveal, rather than saying they
  %are good membranes now?  Then we talk about new membranes at the end of the
  %introduction. Thoughts? I didn't go ahead and make  the change since it
  %needs a bit more thought.  I'm open to other ways to reformulate.  Some of
  %this thinking will percolate into the rest of the introduction as well.
  In this work, we observe transport of water, sodium ions and 20 small polar
  solutes within the pores of a lyotropic liquid crystal (LLC) membrane using
  atomistic molecular simulations. We find that the transport of a species is
  dependent not only on molecular size, but on chemical functionality as well.
  The membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. We observe that all
  solutes perform intermittent hops between lengthy periods of entrapment. Three
  different trapping mechanisms are responsible for this behavior. First, solutes
  that drift out of the pore can become entangled among the dense monomer tails.
  Second, solutes can donate hydrogen bonds to the monomer head groups. Third,
  solutes can coordinate with sodium counter ions.  The degree to which a solute
  is affected by each mechanism is dependent on the chemical functionality of the
  solute. Using the insights developed in this study, we can begin to think about
  how to redesign existing LLC membranes in order to perform solute-specific
  separations.

@@

  %BJC4: generalized to amphiphilic self-assembled structures.
  Under the right conditions, amphiphilic molecules can self-assemble into
  ordered nanostructures that may be capable of performing highly selective
  separations with permeabilities comparable to NF.
  \begin{itemize}
    \item The uniform-sized aqueous pores characteristic of these types of
    systems enforce a molecular-size cut-off, eliminating issues related to the
    polydisperity of NF pores.
    \item In addition to size-exclusion, it may be possible to control the
    chemical environment within the nanopores by altering the identities of the
    hydrophilic moeties that form the pores, affording solute-specific separations.
  \end{itemize}

  %BJC4: bring it back to LLCs but don't make it seem like HII is the best
  Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I 
  bicontinuous (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
  phases.
  \begin{itemize}
	\item When cross-linked, these materials can function as mechanically
	strong separations membranes.
	\item The H\textsubscript{II} phase has hexagonally packed, straight
	pores which is the ideal geometry for high throughtput separations.
	\item However, the synthesis of H\textsubscript{II} membranes with 
	highly aligned hexagonal mesophases has been a challenge that has 
	prevented the material's viability as a separations membrane.
	\item The Q\textsubscript{I} consists of a three dimensional network
	of tortuous and interconnected pores. 
	\item It's more facile synthesis has yielded it more success
	\item The latest Q\textsubscript{I} phase membranes have been shown
	to exhibit selectivities and permeabilities higher than commercial
	RO and NF membranes.
  \end{itemize}

  % Highlight that QI has the best chance.
  Although Q\textsubscript{I} membranes have shown promising results, it
  is not clear how to controllably design them for specific separations
  beyond what has already been achieved.
  \begin{itemize}
    \item Dischinger et al. found that they do not separate purely on the basis
    of size.~\cite{dischinger_effect_2017} 
    \item Empirical modeling revealed correlations between various solute
    physicochemical properties and observed solute rejection. 
    \item Although there was some agreement with their empirical model, it does not
    offer a sufficiently detailed explanation of governing molecular interactions.~\cite{dischinger_effect_2017}
  \end{itemize}

@@

  %BJC4: also edited here to help with the flow.
  In this work, we present studies of the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character within the pores of an H\textsubscript{II} phase LLC. The pores of the 
  H\textsubscript{II} phase have a similar topology to the Q\textsubscript{I} phase but
  is a simpler geometry to model. In future studies, we will extend our techniques to
  the Q\textsubscript{I} phase.

  %BJC4: not sure if I should add a thesis to this paragraph, reattach above, or just
  % leave as is since it's informational.
  Figure~\ref{fig:membrane_rendering} shows an atomistic rendering of the
  membrane in which we placed solutes. We have listed the solutes studied along
  with the abbreviations that we will use in the charts for the remainder of this
  paper in Table~\ref{table:abbreviations}. Note that, in order limit our
  studies to uncharged species, we have only studied acetic acid in its
  protonated form. The pKa of gallic acid is 4.40 while the pKa of acetic acid is
  4.75.~\cite{chuysinuan_gallic_2009,perrin_pka_1981} Assuming that the pKa of
  gallic acid is similar to NaGA3C11, it is possible for our sodium salted
  monomer to exist at the same time as protonated acetic acid. In any case, we
  are more interested in mechanisms of interaction with specific chemical
  functionality more than the behavior of specific molecules.
